Understanding Regional and Temporal Variations in Food Prices: Insights from US Consumer Price Index and Economic Trends

### 2024-11-26 paper/paper.qmd
update paper

---
title: "Understanding Regional and Temporal Variations in Food Prices: Insights from US Consumer Price Index and Economic Trends"
subtitle: "--- TODO: CHANGE --- A Bayesian Approach Reveals the Impact of Economic Indicators and Geographic Disparities on Price Dynamics"
author: 
  - Tanmay Shinde
thanks: "TODO - CHANGE THE LINK - Code and data are available at: [https://github.com/Tanmay-Shinde/Week10Reflection](https://github.com/Tanmay-Shinde/Week10Reflection)."
date: today
date-format: long
abstract: "This paper examines how regional and temporal variations influence food-at-home prices across the United States, and the impact of economic factors such as purchase volume, food categories, and the Consumer Price Index (CPI) on these trends. --- The analysis reveals that while food prices have generally increased iver time, certain categories, such as dairy, fresh produce, and meats, tend to exhibit greater volatility. Factors such as purchase volume, food categories, and the CPI have a considerable influence on these price trends. Notably, higher CPI values correlate with increased food prices, and food categories with higher demand or limited supply exhibit more substantial price fluctuations --- . These findings provide actionable insights for policymakers and stakeholders in food economics, emphasizing the impact of region-specific market conditions and consumer purchasing behaviors on food pricing trends."
format: pdf
number-sections: true
toc: true
bibliography: references.bib
---

@@

# Summary statistics for outcome variable
summary_stats_outcome <- analysis_data %>%
  summarise(
    mean = mean(cpi, na.rm = TRUE),
    median = median(cpi, na.rm = TRUE),
    sd = sd(cpi, na.rm = TRUE),
    min = min(cpi, na.rm = TRUE),
    max = max(cpi, na.rm = TRUE)
)

@@

# Summary statistics for outcome variable
summary_stats_outcome <- analysis_data %>%
  summarise(
    mean = mean(purchaseVolume, na.rm = TRUE),
    median = median(purchaseVolume, na.rm = TRUE),
    sd = sd(purchaseVolume, na.rm = TRUE),
    min = min(purchaseVolume, na.rm = TRUE),
    max = max(purchaseVolume, na.rm = TRUE)
)

>>>>

---
title: "Understanding Regional and Temporal Variations in Food Prices: Insights from US Consumer Price Index and Economic Trends"
subtitle: "--- TODO: CHANGE --- A Bayesian Approach Reveals the Impact of Economic Indicators and Geographic Disparities on Price Dynamics"
author: 
  - Tanmay Sachin Shinde
thanks: "TODO - CHANGE THE LINK - Code and data are available at: [https://github.com/Tanmay-Shinde/Week10Reflection](https://github.com/Tanmay-Shinde/Week10Reflection)."
date: today
date-format: long
abstract: "This paper examines how regional and temporal variations influence food-at-home prices across the United States, and the impact of economic factors such as purchase volume, food categories, and the Consumer Price Index (CPI) on these trends. --- The analysis reveals that while food prices have generally increased iver time, certain categories, such as dairy, fresh produce, and meats, tend to exhibit greater volatility. Factors such as purchase volume, food categories, and the CPI have a considerable influence on these price trends. Notably, higher CPI values correlate with increased food prices, and food categories with higher demand or limited supply exhibit more substantial price fluctuations --- . These findings provide actionable insights for policymakers and stakeholders in food economics, emphasizing the impact of region-specific market conditions and consumer purchasing behaviors on food pricing trends."
format: pdf
number-sections: true
toc: true
bibliography: references.bib
---

@@

# Summary statistics for cpi
summary_stats_outcome <- analysis_data %>%
  summarise(
    mean = mean(cpi, na.rm = TRUE),
    median = median(cpi, na.rm = TRUE),
    sd = sd(cpi, na.rm = TRUE),
    min = min(cpi, na.rm = TRUE),
    max = max(cpi, na.rm = TRUE)
)

@@

# Summary statistics for purchase volume variable
summary_stats_outcome <- analysis_data %>%
  summarise(
    mean = mean(purchaseVolume, na.rm = TRUE),
    median = median(purchaseVolume, na.rm = TRUE),
    sd = sd(purchaseVolume, na.rm = TRUE),
    min = min(purchaseVolume, na.rm = TRUE),
    max = max(purchaseVolume, na.rm = TRUE)
)
